### 2022-01-18 src-latex/parts/50-xp-setup.tex

\begin{figure}[tb]
\includegraphics[width=\linewidth]{figs/protocol.pdf}
\caption{Scheme of the evaluation protocol.}
\label{fig.protocol}
\end{figure}

@@

\subsubsection{OCR system parameters}
\nathalie{Y a-t-il des précisions à ajouter sur la façon dont ont été utilisés les OCR? Ou bien ce sont les versions "sur étagère" qui ont servi?}
\begin{itemize}
    \item Tesseract 4
    \item Pero
\end{itemize}

>>>>

\begin{figure}[tb]
\includegraphics[width=\linewidth]{figs/protocol.pdf}
\caption{Scheme of the evaluation protocol. \joseph{Missing "Ground truth" for NER stage?}}
\label{fig.protocol}
\end{figure}

@@

\subsubsection{OCR system parameters}
\nathalie{Y a-t-il des précisions à ajouter sur la façon dont ont été utilisés les OCR? Ou bien ce sont les versions "sur étagère" qui ont servi?}
\joseph{Totalement sur l'étagère. On a normalisé un peu les données après, c'est tout.}
\begin{itemize}
    \item Tesseract 4.1.1 (newest version: 5, released Nov. 2021)
    \item Pero OCR version from git repo, master branch updated on Sep 15, 2021 % 8b20f29    
    \item other?  % kraken if times allows
\end{itemize}

Pero OCR uses ParseNet \joseph{TODO ref} as internal layout parser for line detection.
Pero OCR uses an LSTM engine \joseph{TODO check + ref} for text line recognition.
Pero OCR generally works very well, as long as the bounding boxes of the regions to recognize are not too tightly adjusted.
Trained on newspapers in European languages by its development team.
Can output results in Latin, Greek and Cyrillic scripts, as well as some commonly-used typographic symbols.

% PERO refs
% O Kodym, M Hradiš: Page Layout Analysis System for Unconstrained Historic Documents. ICDAR, 2021.
% M Kišš, K Beneš, M Hradiš: AT-ST: Self-Training Adaptation Strategy for OCR in Domains with Limited Transcriptions. ICDAR, 2021.
% J Kohút, M Hradiš: TS-Net: OCR Trained to Switch Between Text Transcription Styles. ICDAR, 2021.
